Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023

### 2024-09-27 paper/paper.qmd
add some description

Although there have been studies showing the relationship between crime and economic conditions and population growth, there is still a lack of in-depth research on the dynamics of crime in different communities, especially the dynamic relationship between population density, Covid-19 and crime rates. This study will fill this gap through data analysis. This study obtains the crime data of various communities from 2014 to 2023 according to the method described in @sec-data-overview, especially the data of theft and assault rates. Through these data, this paper analyzes the change trend of crime rates in different communities during these years. The differences between community size and crime rate and the fluctuations in different time periods are discussed. In addition, The research focuses on the dynamic change of crime rate in different communities before and after the epidemic (@fig-theft-rate-trend-2014-to-2023 and @fig-Box-plot-of-theft-rates) and the relationship between population density and crime rates in 2023 (@fig-population-and-assault-rate and @fig-Bar-chart-2023-theft-rates). By assessing these dynamics, this study not only informs law enforcement and urban planners in Toronto, but also in other cities facing similar crime rate challenges, particularly in terms of resource allocation and crime prevention in high-risk neighborhoods.

@@

@@

@@

>>>>

Although there have been studies showing the relationship between crime and economic conditions and population growth, there is still a lack of in-depth research on the dynamics of crime in different communities, especially the dynamic relationship between population density, Covid-19 and crime rates. This study will fill this gap through data analysis. This study obtains the crime data of various communities from 2014 to 2023 according to the method described in @sec-data-overview, especially the data of theft and assault rates. Through these data, this paper analyzes the change trend of crime rates in different communities during these years. The differences between community size and crime rate and the fluctuations in different time periods are discussed. In addition, The research focuses on the dynamic change of crime rate in different neiborhood before and after the Covid-19 (@fig-theft-rate-trend-2014-to-2023 and @fig-Box-plot-of-theft-rates) and the relationship between population density and crime rates in 2023 (@fig-population-and-assault-rate and @fig-Bar-chart-2023-theft-rates). By assessing these dynamics, this study not only informs law enforcement and urban planners in Toronto, but also in other cities facing similar crime rate challenges, particularly in terms of resource allocation and crime prevention in high-risk neighborhoods.

@@

### Sample of part of cleaned data

@@

### crime rate before and after the Covid-19

@@

### relationship between population density and crime rates
